---
title: "case_study"
output: html_document
date: "2023-10-10"
---
```{r}
library(tidyverse)
library(ggridges)
```

```{r}
library(p8105.datasets)

data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb %>% 
  rename(borough = neighbourhood_group) %>% 
  mutate(stars = review_scores_location / 2)
```

## brainstorm questions

- where are airnbnbs most expensive 
  - borough? neighborhood?
- how long are airbnbs active
  - are airbnbs illegal and do they get shut down
- which units have the most avaliabilty 
- how is review score impacted by location
- how many apts are run by one host
  - does that affect price
  - does that vary by neighborhood
- where are airbnbs
  - borough? neighborhood?
  - latitude, longitude 

## attempt solutions

price by borough 
```{r}
nyc_airbnb %>% 
  count(borough)

nyc_airbnb %>% 
  group_by(borough, room_type) %>% 
  summarize(mean_price = mean(price)) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )

nyc_airbnb %>% 
  group_by(borough, room_type) %>% 
  summarize(median_price = median(price)) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = median_price
  )

nyc_airbnb %>% 
  filter(price < 1000, room_type == "Entire home/apt") %>% 
  ggplot(aes(x = price)) + 
  geom_histogram()+
  facet_grid(. ~ borough)

nyc_airbnb %>% 
  filter(price < 1000,
         room_type == "Entire home/apt",
         borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(
    n_apt = n(),
    mean_price = mean(price)) %>% 
  arrange(mean_price)

 nyc_airbnb %>% 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") %>% 
   mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
   ggplot(aes(x = neighbourhood, y = price))+
   geom_boxplot()
 
  nyc_airbnb %>% 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") %>% 
   mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
   ggplot(aes(x = price, y = neighbourhood))+
   geom_density_ridges()
   
```

 ## try to make a map
 
```{r}
 nyc_airbnb %>% 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") %>% 
  ggplot(aes(x = lat, y = long, color = price))+
  geom_point()
```
 
## try something else entriely 

```{r}
library(leaflet)

nyc_airbnb %>% 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") %>% 
  sample_n(500) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(~lat, ~long)
 
nyc_airbnb %>% 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") %>% 
  sample_n(500) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(~lat, ~long, radius = .5)
 
nyc_airbnb %>% 
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") %>% 
  sample_n(500) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = .5)
```

